An agent-based model for city networks based on interactions between firms

### 2019-10-27 main.tex
Update on Overleaf.
.

\textit{find some indicators for polarization : when big cities take everything or when local clusters organize}

Network indicators:

\begin{itemize}
    \item weighted degree distribution (\textit{if it is fat-tailed, log-log power law exponent and adjusted r-squared})
\end{itemize}

Sector structure indicators:

\begin{itemize}
    \item sector diversity (Herfindhal ?) 
\end{itemize}

@@

The model is implemented in NetLogo and integrated into the OpenMOLE platform for model exploration \cite{reuillon2013openmole}.

@@

>>>>

\subsubsection{Geographical indicators:}

\begin{itemize}
    \item Internationalisation (modularity of countries in the network)
    \item Metropolisation (correlation between weighted degree and city size)
    \item Regionalisation (correlation between length and flow of links, stratified by size of extremities)
    \item Specialisation (correlation between sector proximity and flow of links, stratified by size of extremities)
\end{itemize}

\subsubsection{Network and flows indicators:}

%  networkModularity, networkAvgCommunitySize, networkDegreeHierarchy, networkAvgDegree, networkDegreeEntropy, flowsHierarchy, flowsEntropy, rhoDegreeSize, rhoFlowDistancePos, rhoFlowDistance

\begin{itemize}
    \item Louvain modularity, community sizes
    \item Degree and flows distribution (average, hierarchy, entropy)
    \item Correlations (degree-size, flow-distance)
\end{itemize}

% possible other indics:
% weighted degree distribution (\textit{if it is fat-tailed, log-log power law exponent and adjusted r-squared})
%Sector structure indicators: sector diversity (Herfindhal ?)

@@

The model is implemented in NetLogo and integrated into the OpenMOLE platform for model exploration \cite{reuillon2013openmole}. NetLogo provides a good compromise between performance and interactive prototyping and exploration.
%We use in particular data structures providing good performances for the type of operations needed (matrices operations for the construction of the utility function e.g.).

%%%%%%%%%%%%%
\begin{figure}
    \includegraphics[width=0.48\textwidth]{figures/ex_alleq-highgravity_seed-12102_t1500.png}\hspace{0.1cm}
    \includegraphics[width=0.48\textwidth]{figures/ex_alleq-lowgravity_seed-12102_t1500.png}	
    \caption{Example of simulated networks at $t=1500$, with a high (resp. low) gravity decay parameter on the left (resp. right).\label{fig:example}}
\end{figure}
%%%%%%%%%%%%%

@@

\paragraph{One factor sampling}
% 20190924_162740_ONEFACTOR_REPLICATIONS_SYNTHETIC_GRID

\begin{figure}
	\includegraphics[width=0.48\textwidth]{figures/internationalization-gravityDecay_errorbars.png}
    \includegraphics[width=0.48\textwidth]{figures/rhoDegreeSize-gravityDecay_errorbars.png}\\

\end{figure}
